---
title: "SimulationAnalysis"
author: "Dan Guo"
date: "2/27/2021"
output: 
  html_document:
       toc: true
       toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
```

## Read mono peak data and deconvoluted data

Read mono peak data of centroid mode from .imzML file and load spectra of deconvoluted data from .tsv file

```{r}
library('Cardinal')
mono = readMSIData('/Users/danguo/Documents/phd/SpatialStein/Simulations/lipid_MSI_centroid_mode.imzML')
spec = read.table('/Users/danguo/Documents/phd/SpatialStein/Simulations/deconvolution_results/deconvolution_results_centroid.tsv', sep = '\t', header = TRUE, row.names = NULL)

deconv = mono[1:8,]
spectra(deconv) = t(spec[,3:10])
```

## Multivariate Segmentation

Segment the mono peak data and deconvoluted data using spatial centroid segmentation, K = 5

```{r }
set.seed(123)
ssc = spatialShrunkenCentroids(mono, k=5, s=3)
image(ssc, main = 'Mono Peak')
ssc2 = spatialShrunkenCentroids(deconv, k=5, s=3)
image(ssc2, main = 'Deconvoluted Peak')
```

Segment the mono peak data and deconvoluted data using spatial centroid segmentation, K = 3

```{r }
ssc = spatialShrunkenCentroids(mono, k=3, s=3)
image(ssc, main = 'Mono Peak')
ssc2 = spatialShrunkenCentroids(deconv, k=3, s=3)
image(ssc2, main = 'Deconvoluted Peak')
```






## Single ion segmentation using spatial DGMM

```{r}
source('~/Documents/phd/SpatialStein/DSDGMM/model.R')
sp_ratio=1
radius=1
w<-W_matrix(mono,sp_ratio=sp_ratio,radius=1)
w2<-w[[2]]
w<-w[[1]]
```


### Mono Peak: Gaussian Mixture Model

```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
f = 1
kmax=5
out=10
kprior=0
set.seed(333)
gmm<-GMM(msset=mono,f=f,kmax=kmax,out=out,kprior=0)
k<-gmm[[2]]

```

### Mono Peak: Spatial DGMM

```{r}
sdgmm<-DGMM(mono, w=w, w2=w2, k=k, f=f, sp_ratio=sp_ratio,step=1e5,iteration=2000,Annl=0, sig=0.2,initialization="km")
xx<-apply(sdgmm[[10]],1, function (x) which(x==max(x)))
ssc@resultData@listData[[1]]$cluster<-as.factor(xx)
image(ssc, col=cbPalette[1:3], key=FALSE,asp=1, main = paste0(mz(mono)[f],"Mono Peak"))
```

### Deconvoluted peak: Gaussian Mixture Model

```{r}
f = 8
gmm<-GMM(msset=deconv,f=f,kmax=kmax,out=out,kprior=0)
k<-gmm[[2]]

```

```{r}
sdgmm<-DGMM(deconv, w=w, w2=w2, k=k, f=f, sp_ratio=sp_ratio,step=1e5,iteration=2000,Annl=0, sig=0.2,initialization="km")
xx<-apply(sdgmm[[10]],1, function (x) which(x==max(x)))
ssc@resultData@listData[[1]]$cluster<-as.factor(xx)
image(ssc, col=cbPalette[1:3], key=FALSE,asp=1, main = paste0(colnames(spec)[f+3],"Deconvolutead Peak"))
```

## Segmentation accuracy using Gaussian Mixture Model

```{r}
tmp = ssc@resultData@listData[[1]]$class
accu_mono <- c()
for (i in 1:dim(mono)[1])
{
f = i
set.seed(333)
gmm<-densityMclust(spectra(mono)[i,],G=3,modelNames="E")
relt <- table(tmp, gmm$classification)
accu_mono[i] = sum(sort(relt,decreasing = T)[1:k])/dim(mono)[2]
}
#hist(accu_mono)

accu_deconv <- c()
for (i in 1:dim(deconv)[1])
{
f = i
set.seed(333)
gmm<-densityMclust(spectra(deconv)[i,],G=3,modelNames="E")
relt <- table(tmp, gmm$classification)
accu_deconv[i] = sum(sort(relt,decreasing = T)[1:k])/dim(deconv)[2]
}
#hist(accu_deconv)

accu = data.frame(accuracy = c(accu_mono,accu_deconv),peak = c(rep('mono',dim(mono)[1]),rep('deconvoluted',dim(deconv)[1])))
theme_set(
  theme_classic() + 
    theme(legend.position = "top")
  )
ggplot(data = accu, aes(accuracy))+
  geom_histogram(aes(color = peak,fill = peak), bins = 50, alpha=0.4)
```
