---
title: "SimulationAnalysis"
author: "Dan Guo"
date: "4/24/2021"
output: 
  html_document:
       toc: true
       toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE, results='hide')
```

## Read mono peak data and deconvoluted data

Read mono peak data of centroid mode from .imzML file and load spectra of deconvoluted data from .tsv file

```{r}
library('Cardinal')
mono = readMSIData('/Users/danguo/Documents/phd/SpatialStein/Simulations/lipid_MSI_centroid_mode.imzML')
spec = read.table('/Users/danguo/Documents/phd/SpatialStein/Simulations/deconvolution_results/deconvolution_results_centroid_MTD0.050000.tsv', sep = '\t', header = T, row.names = NULL)
spec2 = read.table('/Users/danguo/Documents/phd/SpatialStein/Simulations/deconvolution_results/deconvolution_results_centroid_MTD0.200000.tsv', sep = '\t', header = T, row.names = NULL)

deconv0.05 = mono[1:5,]
spectra(deconv0.05) = t(spec[,3:7])

deconv0.2 = mono[1:5,]
spectra(deconv0.2) = t(spec2[,3:7])
```

## Multivariate Segmentation

Segment the mono peak data and deconvoluted data using spatial centroid segmentation, K = 5

```{r }
set.seed(123)
ssc = spatialShrunkenCentroids(mono, k=5, s=3)
image(ssc, main = 'Mono Peak')
ssc2 = spatialShrunkenCentroids(deconv0.05, k=5, s=3)
image(ssc2, main = 'Deconvoluted Peak 0.05')
ssc2 = spatialShrunkenCentroids(deconv0.2, k=5, s=3)
image(ssc2, main = 'Deconvoluted Peak 0.2')
```




## Single ion segmentation using spatial DGMM

```{r}
source('~/Documents/phd/SpatialStein/DSDGMM/model.R')
sp_ratio=1
radius=1
w<-W_matrix(mono,sp_ratio=sp_ratio,radius=1)
w2<-w[[2]]
w<-w[[1]]
```

### Mono Peak: DGMM

```{r}
set.seed(12345)
dgmm <- spatialDGMM(mono, r=2, k=5, method="adaptive")
image(dgmm, model=list(feature=c(2,3,5,6,7)), layout=c(2,3), main='Mono Peaks')

```

### Deconvoluted0.05: DGMM

```{r}
set.seed(12346)
dgmm <- spatialDGMM(deconv0.05, r=2, k=5, method="adaptive")
image(dgmm, model=list(feature=1:5), layout=c(2,3), main='Deconvoluted0.05')

```

### Deconvoluted0.05: DGMM

```{r}
set.seed(12347)
dgmm <- spatialDGMM(deconv0.2, r=2, k=5, method="adaptive")
image(dgmm, model=list(feature=1:5), layout=c(2,3), main='Deconvoluted0.2')

```

## Single ion segmentation using Gaussian Mixture Model

### Mono Peak: Gaussian Mixture Model

```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
mass_list = read.table('/Users/danguo/Documents/phd/SpatialStein/Simulations/lipid_table.tsv', sep = '\t', header = T, row.names = NULL)
mass_list = mass_list$Monoisotopic.mass
f = 1
kmax=5
out=10
kprior=0
set.seed(333)
for (i in 1:length(mass_list))
{
  f = f = which(abs(mz(mono)-mass_list[i])==min(abs(mz(mono)-mass_list[i])))
  gmm<-GMM(msset=mono,f=f,kmax=kmax,out=out,kprior=0)
  k<-gmm[[2]]
  dgmm@resultData[[i]]$class <- as.factor(gmm[[3]])
  
}
image(dgmm, model=list(feature=1:5), values = 'class', layout=c(2,3), main='Mono Peaks')

```



### Deconvoluted peak 0.05: Gaussian Mixture Model

```{r}
set.seed(444)
for (f in 1:5)
{
    
    gmm<-GMM(msset=deconv0.05,f=f,kmax=kmax,out=out,kprior=0)
    k<-gmm[[2]]
    dgmm@resultData[[f]]$class <- as.factor(gmm[[3]])
}
image(dgmm, model=list(feature=1:5), values = 'class', layout=c(2,3), main='Deconvoluted0.05')
```

### Deconvoluted peak 0.2: Gaussian Mixture Model

```{r}
set.seed(555)
for (f in 1:5)
{
    
    gmm<-GMM(msset=deconv0.2,f=f,kmax=kmax,out=out,kprior=0)
    k<-gmm[[2]]
    dgmm@resultData[[f]]$class <- as.factor(gmm[[3]])
}
image(dgmm, model=list(feature=1:5), values = 'class', layout=c(2,3), main='Deconvoluted0.2')

```



