---
title: "SimulationAnalysis"
author: "Dan Guo"
date: "11/08/2021"
output: 
  html_document:
       toc: true
       toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
```

## Read mono peak data and deconvoluted data

Read mono peak data of centroid mode from .imzML file and load spectra of deconvoluted data from .tsv file

```{r}
library('Cardinal')
mono = readMSIData('/Users/danguo/Documents/phd/SpatialStein/Simulations/lipid_MSI_centroid_mode.imzML')
spec = read.table('/Users/danguo/Documents/phd/SpatialStein/Simulations/deconvolution_results_centroid_MTD0.100000.tsv', sep = '\t', header = T, row.names = NULL)
spec2 = read.table('/Users/danguo/Documents/phd/SpatialStein/Simulations/deconvolution_results_centroid_MTD0.200000.tsv', sep = '\t', header = T, row.names = NULL)

deconv0.1 = mono[1:3,]
spectra(deconv0.1) = t(spec[,3:5])

deconv0.2 = mono[1:3,]
spectra(deconv0.2) = t(spec2[,3:5])

mass_list = read.table('/Users/danguo/Documents/phd/SpatialStein/Simulations/lipid_table.tsv', sep = '\t', header = T, row.names = NULL)
mass_list = mass_list$Monoisotopic.mass

f =  c()
for (i in 1:3)
{
  f = c(f, which(abs(mz(mono)-mass_list[i])==min(abs(mz(mono)-mass_list[i]))))
}
mono = mono[f,]
molecule = c('PC.38.1', 'PA.44.0', 'PC.38.0')
```


## Visulaization of ion image of PC.38.1

```{r}
par(mfrow = c(2,2))
image(mono, feature = 1, contrast.enhance = 'histogram', layout = NULL, main = 'mono')
image(deconv0.1, feature = 1, contrast.enhance = 'histogram', layout = NULL, main = 'deconv0.1')
image(deconv0.2, feature = 1, contrast.enhance = 'histogram', layout = NULL, main = 'deconv0.2')

```


## Single ion segmentation using spatial DGMM

```{r}
source('~/Documents/phd/SpatialStein/DSDGMM/model.R')
sp_ratio=1
radius=1
w<-W_matrix(mono,sp_ratio=sp_ratio,radius=1)
w2<-w[[2]]
w<-w[[1]]
```

### Mono Peak: DGMM

```{r}
set.seed(12345)
par(mfrow = c(2,2))
dgmm <- spatialDGMM(mono, r=2, k=5, method="adaptive")
for (i in 1:3)
{
  print(image(dgmm, model=list(feature=i), layout=NULL, main=paste0('mono peak ', molecule[i])))
}

```

```{r}
par(mfrow = c(2,2))
for (i in 1:3)
{
  print(plot(dgmm, model = list(feature=i), layout = NULL, main = paste0('mono peak ', molecule[i])))
}

```

```{r}
mono_est = list()
for (i in 1:3)
{
  print(paste0('The estimation of Gaussain Component for', molecule[i], ' is:'))
  print(dgmm@resultData@listData[[i]]$estimates)
  mono_est[[i]] = dgmm@resultData@listData[[i]]$estimates$mean
}

```



### Deconvoluted 0.1: DGMM

```{r}
set.seed(12346)
par(mfrow = c(2,2))
dgmm <- spatialDGMM(deconv0.1, r=5, k=4, method="adaptive", init = 'kmeans')
for (i in 1:3)
{
  print(image(dgmm, model=list(feature=i), layout=NULL, main=paste0('deconv0.1 ', molecule[i])))
}

```

```{r}
par(mfrow = c(2,2))
for (i in 1:3)
{
  print(plot(dgmm, model = list(feature=i), layout = NULL, main = paste0('deconvoluted0.1 ', molecule[i])))
}

```

```{r}
deconv0.1_est = list()
for (i in 1:3)
{
  print(paste0('The estimation of Gaussain Component for', molecule[i], ' is:'))
  print(dgmm@resultData@listData[[i]]$estimates)
  deconv0.1_est[[i]] = dgmm@resultData@listData[[i]]$estimates$mean
}
```


### Comparison between deconvoluted0.1 and mono peaks

```{r}
library('ggplot2')
library('gridExtra')
data = list()
par(mfrow = c(2,2))
for (i in 1:3)
{
  means = c(mono_est[[i]], deconv0.1_est[[i]])
  means = log(means)
  comps = c(1:length(mono_est[[i]]), 1:length(deconv0.1_est[[i]]))
  group = c(rep('mono', length(mono_est[[i]])), rep('deconv0.1',length(deconv0.1_est[[i]])))
  data[[i]] = data.frame(means = means, comps = comps, group = group)
}

p1 = ggplot(data = data[[1]])+
    geom_point(aes(x = comps, y = means, group = group, color = group))+
    xlab('component')+
    ylab('Mean Intensity (log scale)')
p2 = ggplot(data = data[[2]])+
    geom_point(aes(x = comps, y = means, group = group, color = group))+
    xlab('component')+
    ylab('Mean Intensity (log scale)')
p3 = ggplot(data = data[[3]])+
    geom_point(aes(x = comps, y = means, group = group, color = group))+
    xlab('component')+
    ylab('Mean Intensity (log scale)')
grid.arrange(p1, p2, p3, nrow = 2)

```


### Deconvoluted0.2: DGMM

```{r}
set.seed(12346)
par(mfrow = c(2,2))
dgmm <- spatialDGMM(deconv0.2, r=5, k=4, method="adaptive")
for (i in 1:3)
{
  print(image(dgmm, model=list(feature=i), layout=NULL, main=paste0('deconv0.2 ', molecule[i])))
}

```

```{r}
par(mfrow = c(2,2))
for (i in 1:3)
{
  print(plot(dgmm, model = list(feature=i), layout = NULL, main = paste0('deconvoluted0.2 ', molecule[i])))
}

```

```{r}

for (i in 1:3)
{
  print(paste0('The estimation of Gaussain Component for', molecule[i], ' is:'))
  print(dgmm@resultData@listData[[i]]$estimates)
}
```

## Single ion segmentation using Gaussian Mixture Model

### Mono Peak: Gaussian Mixture Model

```{r, results='hide'}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

par(mfrow = c(2,2))
kmax=4
out=10
kprior=0
set.seed(333)
means = list()
variances = list()
for (i in 1:3)
{

  gmm<-GMM(msset=mono,f=i,kmax=kmax,out=out,kprior=0)
  k<-gmm[[2]]
  dgmm@resultData[[i]]$class <- as.factor(gmm[[3]])
  means[[i]] = gmm[1][[1]]$parameters$mean
  variances[[i]] =  gmm[1][[1]]$parameters$variance$sigmasq
}
for (i in 1:3)
{
  print(image(dgmm, model=list(feature=i), layout=NULL, value = 'class', main=paste0('mono peak ', molecule[i])))
}

```

```{r}

for (i in 1:3)
{
  print(paste0('The estimation of Gaussain Component for', molecule[i], ' is:'))
  print(paste0('mean: ', means[[i]]))
  print(paste0('variance: ', variances[[i]]))
}
```



### Deconvoluted peak 0.1: Gaussian Mixture Model


```{r, results='hide'}
par(mfrow = c(2,2))
means = list()
variances = list()
kmax=4
out=10
kprior=0
set.seed(333)
for (i in 1:3)
{

  gmm<-GMM(msset=deconv0.1,f=i,kmax=kmax,out=out,kprior=0)
  k<-gmm[[2]]
  dgmm@resultData[[i]]$class <- as.factor(gmm[[3]])
  means[[i]] = gmm[1][[1]]$parameters$mean
  variances[[i]] =  gmm[1][[1]]$parameters$variance$sigmasq
}
for (i in 1:3)
{
  print(image(dgmm, model=list(feature=i), layout=NULL, value = 'class', main=paste0('deconv0.1 ', molecule[i])))
}

```

```{r}

for (i in 1:3)
{
  print(paste0('The estimation of Gaussain Component for', molecule[i], ' is:'))
  print(paste0('mean: ', means[[i]]))
  print(paste0('variance: ', variances[[i]]))
}
```


